Towards Verifying the Bitcoin-S Library

### 2019-06-22 paper/paper.tex
Added more text to Pure Scala Fragment

\paragraph{The Pure Scala Fragment.} Stainless supports only a subset
of Scala. \todo{Anna It supports blabla, in particular it supports not
  blablabla. (check class with var)}

@@

They call this Pure Scala.  You can find the specification of Pure
Scala on the Stainless documentation website
\cite{Stainless:documentation} in the section
\href{https://epfl-lara.github.io/stainless/purescala.html}{Pure
  Scala}.

>>>>

\paragraph{The Pure Scala Fragment.} Stainless supports only a subset
of Scala. They call this Pure Scala.  You can find the specification of Pure
Scala on the Stainless documentation website
\cite{Stainless:documentation} in the section
\href{https://epfl-lara.github.io/stainless/purescala.html}{Pure
  Scala}.
\todo{Kai: check the text

It supports Algebraic Data Type definitions in the form of 
Abstract Class and Case Class/Case Object,
inheritance of an Abstract Class by a Case Class/Case Object,
Object for grouping classes and functions,  
short-circuit interpretation of boolean expressions, 
Generics with invariant type parameters and simple hierarchy 
(subclasses define the same type parameters in the same order),
default values of function parameters,
Pattern matching, 
Values,
anonymous classes and more.

As an extension to Pure Scala Stainless supports some imperative features.
It supports 
declaring a variable in a local scope of a function, 
declaring a variable in trait without assigning a default value,
while loops,
case classes with \textit{var} arguments.

In particular Stainless does not support
Class definition,
inheritance by Object,
abstract type members,
variance annotations, upper and lower type bounds in generics,
variables in classes and objects,
private inner classes,
messages as a second argument in the Require function and more.}

@@
